---
title: "p8105_hw1_KAB2310"
author: "Kamiah Brown"
date: "2024-09-16"
output: github_document
---
## This is my submission for Homework 1. 

##Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(tibble)
```

#Problem 1 -- 
## I installed the package 'palmerpenguins' directly in the console. 

## R Markdown
```{r penguins}
data("penguins", package = "palmerpenguins")
nrow(penguins)
ncol(penguins)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
## The penguins dataset has 344 observations and 8 variables. 
## The variables consist of the following: species, island, bill length, bill depth, flipper length, body mass, sex and year. There nrow is 344 and the ncol is 8. 
## The mean flipper length is 200.9152. 

## Creating Scatterplot of Flipper Length vs. Bill Length
```{r penguins}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(x = "Bill Length (mm)", y = "Flipper Length (mm)", title = "Scatterplot of Flipper Length vs Bill Length by Species") 
```

##Saving scatterplot of Bill Length (mm) vs Flipper Length (mm)
```{r}
ggsave("Scatterplot of Bill Length (mm) vs Flipper Length (mm)", plot = scatter_plot, width = 7, height = 5)
```

##Problem 2
```{r random_samp}
df = tibble(
  random_samp = rnorm(10),
  logical_vector = random_samp > 0,
  character_vector = c("january","february", "march", "april", "may", "june", "july", "august", "september", "october"))
factor_vector = factor(c("Level 1", "Level 2", "Level 3", "Level 1", "Level 2", "Level 3", "Level 1", "Level 2", "Level 3", "Level 1"))
```

